Manuscript 1 code

### 2025-02-05 manuscript_1_code.Rmd
removed area calculations, updated functional group csv

# convert cover to area
macro_long_data$area <- macro_long_data$prop_cover*0.25
# write_csv(macro_long_data, here("Data", "macro_long_data.csv"))
```

```{r site macroalgal data}
# NOTE - FRI JAN 24 - updated mean() in summarize across to sum() to reflect new method of calculating cover as area
site_macro <- macroalgae %>%
  dplyr::group_by(year, site, habitat,site_habitat) %>%
  dplyr::summarize(across(acanthophora_spicifera:valonia_ventricosa, \(x) sum(x, na.rm = TRUE)))

@@

alpha_diversity_quad_macro$area <- alpha_diversity_quad_macro$macroalgal_prop_cover*0.25
```

@@

alpha_diversity_site_macro$area <- alpha_diversity_site_macro$prop_cover*0.25
```

@@

```{r read and prep functional group data}
algae_fg_raw2 <- read_csv(here("data","algae_functional_groupings_092724.csv"))

@@

#change species names to be lowercase & have underscore 
algae_fg$species <- gsub(" ", "_", tolower(algae_fg$species))
algae_fg$morphology <- trimws(algae_fg$morphology)
algae_fg$morphology <- gsub(" ", "_", algae_fg$morphology)

>>>>

```{r site macroalgal data}

site_macro <- macroalgae %>%
  dplyr::group_by(year, site, habitat,site_habitat) %>%
  dplyr::summarize(across(acanthophora_spicifera:valonia_ventricosa, \(x) mean(x, na.rm = TRUE)))

@@

@@

@@

```{r read and prep functional group data}
algae_fg_raw2 <- read_csv(here("data","MCR_Algal_Functional_Groups_02042025_updatedtax.csv"))

@@

#change species names to be lowercase & have underscore 
algae_fg$species <- gsub(" ", "_", tolower(algae_fg$species))
algae_fg$morphology <- trimws(algae_fg$functional_grouping_updated)
algae_fg$morphology <- gsub(" ", "_", algae_fg$morphology)
